Lipid Probe Template

### 2025-03-15 IndividualStudies/template_study.qmd
Added template files for the individual studies

---
title: "Farley et al. 2024"
subtitle: "Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function"
format: 
  html:
    embed-resources: false
standalone: false
---

@@

# Opening the datatable for this page IN FINAL RENDER
data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))

@@

{{< include /StudyInformation_includes/SF_2024_A_include.qmd >}}

@@

#### Cell Compartment

@@

>>>>

---
title: "Template based on Farley et al. 2024"
subtitle: "Study title"
format: 
  html:
    embed-resources: false
standalone: false
---

<!-- CHANGE THIS TO POINT TO THE NEW DATASET -->

@@

# Opening the datatable for this page - CHANGE!
data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))

@@

{{< include /StudyInformation_includes/template_include.qmd >}}

@@

<!-- CHANGE THESE  TO NEW VERSION MADE VIA FUNCTIONS IN Resources/Run_GO_DOTplots.R -->
#### Cell Compartment

@@

<!-- CHANGE THIS TO POINT TO THE RIGHT DATA FILE -->

### 2025-03-15 LipidProbe/template_lipidprobe.qmd
Added template files for the individual studies

---
title: "Trifunctional Sphingosine"
format: html
prefer-html: true
callout-icon: false
---

@@

:::{.border}
::: {layout="[[100], [100]]"}
![(A) Native Sphingosine.](/LipidProbe/Structures/Sphingosine.png)

![(B) Trifunctional Sphingosine.](/LipidProbe/Structures/TF_Sphingosine.png)

@@

### Cell background: Huh7

@@

{{< include /StudyInformation_includes/SF_2024_A_include.qmd >}}

@@

<!-- Data wrangling to make the plots -->

@@

#  SF_2024_data <- readr::read_csv("LipidProbe/DataSets/SF_ACS-Chem-Bio_2024_download.csv") |>
#  	filter(LipidProbe == "Sph")

# 	write.csv(SF_2024_data, "LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")

# Opening the datatable for this page
data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
	filter(LipidProbe == "Sph")

@@

<iframe src="/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

@@

(No MF pathways identified among enriched hits and candidates.)

@@

{{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download">}}

>>>>

---
title: "Lipid Probe Template"
format: html
prefer-html: true
callout-icon: false
---

@@

:::{.border}
::: {layout="[[100], [100]]"}
![(A) Native structure.]()

![(B) Trifunctional structure.]()

@@

### Cell background:

@@

{{< include StudyInformation_includes/template_include.qmd >}}

@@

<!-- CHANGE THIS TO POINT TO THE NEW DATASET -->

@@

# Opening the datatable for this page
data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv"))

@@

<!-- CHANGE THIS TO THE CORRECT DOT PLOT, RENDERED VIA FUNCTIONS CALLED IN Resources/Run_GO_DOTplots.R -->
<iframe src="/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

@@

<!-- CHANGE THESE IF THE MF AND BP DOT PLOTS WORK PROPERLY -->
(No MF pathways identified among enriched hits and candidates.)

@@

<!-- CHANGE THIS TO THE CORRECT NEW DATASET -->
{{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download">}}
